Better fusion for filters

### 2014-03-23 2014betterfusionforfilters/section/04-ILP.tex
formalise graph construction
add @cross@ combinator. todo fix up constraint checking

@@

>>>>

\begin{tabbing}
MMMM        \= MM   \= \kill
$nodes$     \> @::@ \> $program \to V$          \\
$edges$     \> @::@ \> $program \to E$          \\
$edge$      \> @::@ \> $\{bind\} \times bind \to E$\\
\\
MMMMM       \= \kill
$nodes(bs)$ \> $= \{(name(b), \tau_b) | b \in bs\}$       \\
\\
$edges(bs)$ \> $= \bigcup_{b \in bs}edge(b)$    \\
\\
MMMM             \= M \= \kill
$edge(bs, out = @fold@~f~in)$ \\
                              \> $=$    \> $\{inedge(bs,out,s) | s \in f\}$ \\
                              \> $\cup$ \> $\{inedge(bs, out, in) \}$       \\
$edge(bs, out = @map@~f~in)$  \\
                              \> $=$    \> $\{inedge(bs,out,s) | s \in f\}$ \\
                              \> $\cup$ \> $\{inedge(bs, out, in) \}$       \\
$edge(bs, out = @filter@~f~in)$  \\
                              \> $=$    \> $\{inedge(bs,out,s) | s \in f\}$ \\
                              \> $\cup$ \> $\{inedge(bs, out, in) \}$       \\
$edge(bs, out = @gather@~data~indices)$  \\
                              \> $=$    \> $\{(out,data, fusion~preventing) \}$ \\
                              \> $\cup$ \> $\{inedge(bs, out, indices) \}$       \\
$edge(bs, out = @cross@~a~b)$            \\
                              \> $=$    \> $\{inedge(bs, out, a) \}$       \\
                              \> $\cup$ \> $\{(out, b, fusion~preventing) \}$ \\
$edge(bs, outs = @external@~ins)$  \\
                              \> $=$    \> $\{(outs,i, fusion~preventing) | i \in ins \}$ \\
\\
$inedge(bs,to,from)$ \\
                     \> $|$ \> $(from = @fold@~f~s) \in bs$     \\
                     \> $=$ \> $(to, from, fusion~preventing)$  \\
                     \> $|$ \> $(\ldots,from,\ldots = @external@ \ldots) \in bs$     \\
                     \> $=$ \> $(to, from, fusion~preventing)$  \\
                     \> $|$ \> $otherwise$                      \\
                     \> $=$ \> $(to, from, fusible)$            \\
\end{tabbing}

@@

\subsection{Subtype optimisations}
For two clusters $i, j$, if $x_{ij} = 0 \vee \tau_i \not= \tau_j$, then $i$'s generator must be fused with $j$ and vice versa, recursively ($x_{ij} = 0 \implies check(i,j)$).
Problem: actually generating constraints for \emph{all} pairs of nodes with unequal types is excessive.
I see two solutions to this:
\begin{itemize}
\item
Generate fewer constraints and rely on transitivity.
This means that for each pair $i,j$ we wouldn't generate an $x_{ij}$ and thus not generate those constraints, unless $i$ or $j$ is a @filter@, or arc between $i$ and $j$.
This would help, but also means we can't \emph{minimise} on these removed $x_{ij}$, so the solution won't count the (rather smaller) benefits of fusing two non-connected nodes.
\item
Alternatively:
we can say, only generate subtype constraints if there is no \emph{fusion preventing path} between $i$ and $j$.
Here, we generate fewer constraints than originally, but still more than above.
We also must preprocess the graph to find such blocking paths.
But we still get the minimisation to count non-connected nodes.
\end{itemize}
